Daily Shelter and Overnight Services Availabilities

### 2024-09-26 paper/paper.qmd
added summary table of means

---
title: "Daily Shelter and Overnight Services Availabilities"
#subtitle: "Marriage Data Cleaning"
author: "Cher Ning-Li"
thanks: "Code and data are available at: https://github.com/cher-ning/shelter_occupancies"
date: today
date-format: long
abstract: "In this paper I analyze the capacity vs real occupancy of shelters across Canada."
#TODO Complete abstract after paper.
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Some of our data is of marriages (@fig-marriages), from @opendatatoronto.

```{r}
#| label: fig-occupancyrate-vs-month
#| fig-cap: Shelter Occupancy Rate in 2024 Over the Months
#| echo: false

#data |> 
#  ggplot(aes(x = date, y = occupancy_rate)) + 
#  geom_point()

hist(data$occupied_beds)
```

@@

# Model

## Model set-up

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

>>>>

---
title: "Daily Shelter and Overnight Services Availabilities"
author: "Cher Ning-Li"
thanks: "Code and data are available at: https://github.com/cher-ning/shelter_occupancies"
date: today
date-format: long
abstract: "In this paper I analyze the capacity vs real occupancy of shelters across Canada."
#TODO Complete abstract after paper.
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Some of our data is of occupancy rate of shelters across the months (@fig-occupancyrate-vs-month), from @opendatatoronto.

#switch to table here
```{r}
#| label: fig-occupancyrate-vs-month
#| fig-cap: Shelter Occupancy Rate in 2024 Over the Months
#| echo: false

rate_means <- data %>% select(month, occupancy_rate) %>% group_by(month) %>% 
  summarise(mean_occupancy_rate = mean(occupancy_rate))

knitr::kable(rate_means, align ="c", col.names= c("Month", "Mean Occupancy Rate"))

```
# add summary table of funding capacity here
```{r}
#| label: fig-fundingcapacity-summary
#| fig-cap: Funding Capacities of Toronto Emergency Shelters
#| echo: false

summary(data$funding_capacity)
```

```{r}
#| label: fig-fundingcapacity-histogram
#| fig-cap: Funding Capacities of Toronto Emergency Shelters
#| echo: false

hist(data$funding_capacity)
```

@@
